% Complete recipe example
\begin{recipe}
[% 
    preparationtime = {\unit[2]{h}},
    portion = {\portion{5-6}},
    source = {Mum}
]
{Lor ark}
   
    \introduction{%
        Traditional teochew duck from mums childhood.
    }
    
    \ingredients{%
        1 & Large duck\\
        3 tbsp & Sea salt\\
        1 tbsp & Five spice powder\\
        2 tbsp & Black soy sauce\\
%        \textbf{Braising sauce}\\
        \unit[40]{g} & White sugar\\
        \unit[100]{g} & Galangal (cut into thick slices)\\
        $\frac{1}{2}$ tsp & Five spice powder\\
        2 & Cinnamon sticks\\
        2 & Star anises\\
        4 & Cloves\\
        5 cloves & Garlic\\
        1 to 1.5 cups & Dark soy sauce\\
        1 cup & Light soy sauce\\
        Water\\
        Salt/sugar\\
%        \textbf{Garlic chilli vinegar} (never tried)
        7 cloves & Garlic\\
        2 & Birdseye chillies\\
        10 tbsp & White vinegar\\
%        \textbf{Additional}\\
        10 & Hardboiled eggs\\
        1 & Sliced cucumber
    }
    
    \preparation{%
        \step Rub salt over the whole duck and let it marinate for half an hour or more to get rid of some of its odour.
        \step Wash off salt and also wax from the under wing and thighs of the duck and remove any feathers. Drain well.
        \step Rub the black soya sauce and five spice powder all over the duck including the cavity and let it marinate for an hour.
        \step Hardboil the eggs and set aside.
        \step Heat up wok and add sugar till caramelized.
        \step Transfer duck and coat the breast side first with the caramelized sugar and then turn to the other side and repeat till the whole duck is nicely coated with the sugar.
        \step Then turn back the duck, breast side down and add the rest of the ingredients.
        \step Bring to boil and lower to medium heat, cover and let it braise for an hour. Turn the duck every \unit[30]{mins}.
        \step Add the hardboiled eggs in. Turn the duck again and braise for another \unit[10]{mins}. Meat usually good now, if you want it to be softer then braise for another \unit[10]{mins}. 
        \step Let the duck rest for at least an hour or more in the sauce.
        \step Combine all the ingredients for the dipping sauce and mix well.
        \step Then take it out from the gravy and drain before cutting it into pieces. Transfer them on a serving plate.
        \step Cut any additional ingredients such as eggs, gizzards or bean curd puff and transfer them to the same serving plate as the duck and pour some gravy over them and garnish. Goes well with the traditional garlic chilli vinegar dipping sauce.
    }
       
    \hint{%
        Can cook noodles in the sauce after.
    }
    
\end{recipe}
