% Complete recipe example
\begin{recipe}
[% 
    preparationtime = {\unit[2]{h}},
    source = {Website with music}
]
{Kimchi}
   
    \introduction{%
        Korean favourite. Tastes delicious and can basically be eaten with any rice dish. Fermented stuff is good for you.
    }
    
    \ingredients{%
        1 & Medium head (1kg) wombok\\
        $\frac{1}{4}$ cup & Salt\\
        & Water\\
        1 tbsp & Grated garlic (5 to 6 cloves)\\
        1 tsp & Grated ginger\\
        1 tsp & Sugar\\
        3 tbsp & Fish sauce\\
        5 tbsp & Gochugaru (korean red chilli flakes)\\
        \unit[250]{g} & Daikon (white radish) peeled and cut into 2.5cm strips\\
        4 & Spring onions cut into \unit[2.5]{cm} strips
    }
    
    \preparation{%
        \step Cut the cabbage lengthwise into quarters and remove the cores. Cut each quarter crosswise into \unit[5]{cm} wide strips.
        \step Place the cabbage and salt in a large bowl. Mix until it softens, then add water to cover the cabbage. Put a plate on top and weigh it down. Let stand for 1 to 2 hours.
        \step Rinse the cabbage under cold water and drain in a colander for 15 to 20 minutes. Rinse and dry the bowl you used for salting, and set it aside to use in step 5.
        \step Make the paste: combine the garlic, ginger, sugar, and fish sauce in a small bowl and mix to form a smooth paste. Mix in the gochugaru, using 1 tbsp for mild and up to 5 tbsp for spicy.
        \step Squeeze any remaining water from the cabbage and return it to the bowl along with the radish, scallions, and seasoning paste.
        \step Mix paste with the vegetables until they are coated.
        \step Pack the kimchi into the jar, pressing down on it until the brine rises to cover the vegetables. Leave at least \unit[2.5]{cm} at the top. Seal the jar with the lid.
        \step Let the jar stand at room temperature for 3 to 5 days.
        \step Check the kimchi daily, pressing down on the vegetables to keep them submerged under the brine and release the gases.
        \step When ready refrigerate.
    }
   
    \hint{%
        Can add other vegetables such as 2 carrots. Just make sure it is cut into a rectangular prism.
        }

\end{recipe}
