% Complete recipe example
\begin{recipe}
[% 
    portion = {\portion{40-50 pieces}},
    source = {Internet}
]
{Kuih loyang}
   
    \introduction{%
        Traditional Malay kuih. Honeycomb biscuits.
    }
    
    \ingredients{%
        \unit[400]{mL} & Coconut milk\\
        \unit[200]{g} & All-purpose flour\\
        \unit[200]{g} & Rice flour\\
        2 & Large eggs\\
        \unit[170]{g} & Sugar\\
        \unit[200]{mL} & Water\\
        $\frac{1}{2}$ tsp & Salt\\
        & Oil for deep frying
    }
    
    \preparation{%
        \step Add coconut milk, eggs, sugar, water and salt in a mixing bowl and mix until well combined and all sugar are dissolved.
        \step Sift and all all-purpose flour and rice flour into the mixture. Whisk until well combined with no lumps. If is too thick, add one tablespoon of water at a time until the mixture resembling of a pancake batter.
        \step Heat up oil in a wok/saucepan on medium heat. Tips: dip a wooden chopstick into the hot oil, if the chopstick is bubbling up, it is ready.
        \step Preheat brass moulds in the hot oil, about 2-3 minutes. (The moulds have to be hot enough for batter to cling on them)
        \step CAUTIOUS: Dip hot mould into batter for 10 seconds. Make sure batter coats only the bottom and sides of mould, never over the top.
        \step Slowly lift it up and dip mould back in hot oil. Shake to release from mould and fry until golden brown on both sides.
        \step Take it out from hot oil, and let it cool over paper towel to soak up all the oil.
        \step Repeat until all batter is used up. Store in air-tight containers.
    }
       
\end{recipe}
